\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
Results restructuring

We find that the model using ontology-based features
(\textit{OntoPred}) is showing significantly\todo{significance test
  and p value? otherwise remove} better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in significantly\todo{p-val}
increased performance when incorporating the PPI graph, demonstrating
that these features localize on the PPI network whereas the molecular
features do not.

, while also only \textit{OntoPred} shows significant performance increase when adding \textit{GENConv} graph convolutional neural layers over the PPI graph. However, graph convolutional neural layers such as \textit{GCNConv} and \textit{GENConv}, especially when incorporated into the proposed \textit{ResGraphConv} blocks, add a lot of learnable parameters to the network, leading to more expressive power. This may lead to better performance, while deceiving, whether the respective features actually localize on the PPI graph.

To eliminate these options we rebuild the graph model, whilst removing all graph convolutional neural layers in the residual blocks. This pruned network, with no information on the protein--protein interactions, reached very similarly results, as the original \textit{OntoPred} model. Secondly, when substituting the original \textit{GENConv} layers with \textit{GCNConv} or other related layers in the graph convolutional step of the ResGraphConv blocks, this model would achieve once again no significant performance gain in comparison to the plain \textit{OntoPred} one. This performance increase was only noticeable for \textit{GENConv} layers. The discrepancy of \textit{GENConv} and \textit{GCNConv} may be founded in numerical stability and fading signals, as described in the introduction of both methods.

As this performance increase is quite significant, we \textbf{conclude that protein function does localize while molecular features do not (BETTER FORMULATION)}. ...

>>>>

We find that the model using ontology-based features
(\textit{OntoPred}) is showing significantly\todo{significance test
  and p value? otherwise remove} better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in significantly\todo{p-val}
increased performance when incorporating the PPI graph.  This increase
can be observed with different graph neural network
architectures\todo{data not in the table}. While the {\em GCNConv} and
{\em GENConv} architecture already shows an improvement, the
\textit{ResGraphConv} blocks add a large amount of additional
learnable parameters to the network, leading to more expressive
power. To test whether the improvement is due to the number of
learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are
removed\todo{is this still a graph model?}. This pruned network, with
no information on the protein--protein interactions, reached very
similarly results as the original \textit{OntoPred} model\todo{data
  not shown; and details missing from Methods} and showed no
improvement.

\todo[inline]{Not clear, need to reformulate:}
Furthermore, when substituting the original \textit{GENConv} layers with \textit{GCNConv} or other related layers in the graph convolutional step of the ResGraphConv blocks, this model would achieve once again no significant performance gain in comparison to the plain \textit{OntoPred} one. This performance increase was only noticeable for \textit{GENConv} layers. The discrepancy of \textit{GENConv} and \textit{GCNConv} may be founded in numerical stability and fading signals, as described in the introduction of both methods.

As the inclusion of graph information significantly\todo{p val}
increases performance, we conclude that information about protein
functions localizes on the graph while molecular features do not.
